Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-11-07 Papers/InProgress/NaturalDeduction/GodProof-ND.tex

\bibitem[{\itshape Bj{\o}rdal(1999)}]{bjordal}
Bj{\o}rdal, F. 1999. Understanding G\"odel's Ontological Argument, in Timothy Childers (ed.) The Logica Yearbook 1998, pp. 214-217, Filosofia.

@@

\bibitem[{\itshape Fuhrmann(2005)}]{fuhrmann}
Fuhrmann, A. 2005.
Existenz und Notwendigkeit -- Kurt G\"odel's Axiomatische Theologie, in Olsson e.J., Schr\"oder-Heister, P. and Spohn, W. (eds.) Logik in der Philosophie, pp. 349-374, Synchr.-Wissenschafts-Verlag.

@@

\bibitem[{\itshape G\"odel(1970)}]{Goedel} 
G\"odel, K. Ontological Proof. In Kurt G\"odel Collected Works vol. III. Ed. Feferman et al., pp. 403--404, 139, 145 or {\itshape Appendix A. Notes in Kurt G\"odel's hand} in [Sobel 2001].

\bibitem[{\itshape Hajek(1996)}]{hajek}
Hajek, P. 1996. Magari and others on G\"odel's Ontological Proof, in Ursini et alii
(eds.) Logic and Logical Algebra, pp. 125--136, Marcel Dekker.

@@

\bibitem[{\itshape Muskens(2006)}]{Muskens}
Muskens, R. 2006. {\itshape Higher Order Modal Logic}. In P. Blackburn, J.F.A.K. van Benthem, and F. Wolter, editors, Handbook of Modal Logic, Studies in Logic and Practical Reasoning, pages 621-653. Elsevier, Dordrecht, 2006.

@@

\bibitem[{\itshape Paulin-Mohring(2015)}]{coq} Paulin-Mohring, C. 2015. {\itshape Introduction to the calculus of inductive constructions}. In %D. Delahaye and B. Woltzenlogel Paleo, editors, 
All about Proofs, Proofs for All,
Mathematical Logic and Foundations. College Publications, London.

@@

>>>>

\bibitem[{\itshape Bj{\o}rdal(1999)}]{bjordal}
Bj{\o}rdal, F. 1999. Understanding G\"odel's Ontological Argument. Ed. Childers, T. The Logica Yearbook 1998, pp. 214-217, Filosofia.

@@

\bibitem[{\itshape Fuhrmann(2005)}]{fuhrmann}
Fuhrmann, A. 2005.
Existenz und Notwendigkeit -- Kurt G\"odel's Axiomatische Theologie. Eds. Olsson e.J., Schr\"oder-Heister, P. and Spohn, W. Logik in der Philosophie, pp. 349-374, Synchr.-Wissenschafts-Verlag.

@@

\bibitem[{\itshape G\"odel(1970)}]{Goedel} 
G\"odel, K. Ontological Proof. In Kurt G\"odel Collected Works vol. III. Ed. Feferman, S. et al., pp. 403--404, 139, 145 or {\itshape Appendix A. Notes in Kurt G\"odel's hand} in [Sobel 2001].

\bibitem[{\itshape Hajek(1996)}]{hajek}
Hajek, P. 1996. Magari and others on G\"odel's Ontological Proof. Eds. Ursini et al. Logic and Logical Algebra, pp. 125--136, Marcel Dekker.

@@

\bibitem[{\itshape Muskens(2006)}]{Muskens}
Muskens, R. 2006. {\itshape Higher Order Modal Logic}. Eds. Blackburn, P. \& van Benthem, J.F.A.K. \& Wolter, F. Handbook of Modal Logic, Studies in Logic and Practical Reasoning, pages 621-653. Elsevier, Dordrecht, 2006.

@@

\bibitem[{\itshape Paulin-Mohring(2015)}]{coq} Paulin-Mohring, C. 2015. {\itshape Introduction to the calculus of inductive constructions}. Eds. Delahaye, D. \& Woltzenlogel Paleo, B. 
All about Proofs, Proofs for All,
Mathematical Logic and Foundations. College Publications, London.

@@

TODO: Check paper published in Logica Universalis 2016. 
TODO: 2013a lacks editors. Same for 2015b. 2015c.
